Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
Edit background section

Aside from \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501} that consider the task of ASSR, much of the work dedicated to acoustic scene modeling is applied to the ASC tasks.

Thus, studying the first DCASE challenge \cite{barchiesi2015acoustic} in 2013 is convenient as it concentrates much of the effort for this latter task. The table \ref{tab:dcase} summarizes the different algorithmic choices taken by the teams where most of scene predictions are achieved by majority voting of predictions over features.

\begin{table}
\begin{center}
\caption{Designs submitted to the DCASE2013 ASC challenge. RQA stands for recurrence quantification analysis, ILD for inter-aural differences and UL for unsupervised learning.  \label{tab:dcase}}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\cite{olivetti2013wonder} OE & 17 & compression distance, Random Forests \\
\cite{elizalde2013vector} ELF & 55 & I vector, LDA \\
\cite{krijnders2013tone} KH & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} PE & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} NHL & 60 & UL of Mel spectra, SVMs \\
\cite{nogueira2013sound} NR1 & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} CHR & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} GSR & 69 & Mel and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} RG & 69  & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} LTT & 72 & MFCCs, Tree baggers \\
\cite{roma2013recurrence} RNH & 76 & RQA features stacked with MFCCs, SVMs \\
\end{tabular}
\end{center}
\end{table}

In this paper, we are interested in evaluating different algorithmic designs leading to different scene models, we therefore resort to straightforward ranking performance measures for the ASSR task. Also, we resort to the use of SVMs with default parameters ($C=1$) for computing classification accuracy for the ASC task, as SVMs are widely used in the community and allows us to better root our work and focus our performance analysis on the earlier processing stages. Moreover, since the MFCCs are well established features and perform well in this task, they will be thoroughly used as baselines features in the experiments described in this paper.

@@

For most of the experiments reported in this paper, the DCASE2013 datatset is considered \cite{giannoulis2013database, 7100934}. To build this dataset, three different recordists visited a wide variety of locations in Greater London over
a period of months and in each
scene recorded a few minutes of audio for each scene type. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type.
The dataset is split into a public dataset that can used for optimizing the ASC system and a private dataset used for computing the resulting accuracy using a 5 fold cross validation scheme. The folds used in this paper are the same as the ones used during the challenge.

As of today, there exist larger publicly available dataset, the
Rouen dataset \cite{rakotomamonjy2015histogram} and the dCase2016 \cite{Mesaros2016_EUSIPCO} (only the public part). The latter is also considered in this paper as a validation of the proposed approach.

As studied in \cite{lagrange:hal-01082501}, the DCASE2013 dataset has interesting intra class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices. Also, it is still challenging as state-of-the-art systems based on features design and support vector machines (SVMs) achieves 76 \% \cite{roma2013} (winner of the 2013 challenge RQA+SVM). For the sake of comparison the HOG+SVM approach \cite{rakotomamonjy2015histogram} achieves 75 \% and 92 \% on the dcase2013 and the Rouen datasets respectively. On the former, recent advances using hierarchical classifiers architectures reports 84 to 87 \% of accuracy depending on the prior knowledge considered for building the classifier architecture \cite{phan2016label}. On the latter, the state-of-the-art is currently 95 \% \cite{bisot2016acoustic}.

In this paper, we shall demonstrate that the use of features based on the wavelet scattering together with object-based representation of the acoustic scene allows us to achieve interesting performance both in the ASSR and ASC paradigms.

>>>>

Aside from \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501} that consider the task of ASSR, much of the work dedicated to acoustic scene modeling is applied to the ASC tasks. \ja{Since we go into so much detail on ASC, shouldn't we at lest describe what these works do? Some of this is already described in the motivations section, so perhaps we should move some over in here?}
An overview of the efforts for the latter task is provided by the DCASE2013 challenge \cite{barchiesi2015acoustic}, held in 2013 to compare differrent approaches to scene classification. Table \ref{tab:dcase} summarizes the results of the submitted algorithms where most \ja{?} of scene predictions are achieved by majority voting of predictions over features. \ja{What about the other algorithms? Why are we excluding them here?}

\begin{table}
\begin{center}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\cite{olivetti2013wonder} OE & 17 & compression distance, random forests \\
\cite{elizalde2013vector} ELF & 55 & i-vector, LDA \\
\cite{krijnders2013tone} KH & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} PE & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} NHL & 60 & UL of mel spectra, SVMs \\
\cite{nogueira2013sound} NR1 & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} CHR & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} GSR & 69 & mel \ja{?} and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} RG & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} LTT & 72 & MFCCs, tree baggers \\
\cite{roma2013recurrence} RNH & 76 & RQA features stacked with MFCCs, SVMs \\
\end{tabular}
\end{center}
\caption{Designs submitted to the DCASE2013 ASC challenge. RQA stands for recurrence quantification analysis, ILD for inter-aural differences and UL for unsupervised learning. \label{tab:dcase}}
\end{table}

In this paper, we are interested in evaluating different algorithmic designs leading to different scene models, we therefore resort to straightforward ranking performance measures for the ASSR task. \ja{It's not clear to me how the first part implies the second part here} Similarly, we have picked linear SVMs as our classifier for the ASC task, since these are a standard tool in the community and allows for us to focus our analysis on the earlier processing stages. Moreover, since MFCCs are well-established features which perform well for these task, we shall include them baseline features in all experiments described in this paper.

@@

For most of the experiments reported in this paper, we will consider the DCASE2013 dataset \cite{giannoulis2013database, 7100934}. To build this dataset, three different recordists visited a wide variety of locations in Greater London over
a period of several months and in each
scene recorded a few minutes of audio. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type.
The dataset is split into a public dataset that can used for optimizing the ASC system and a private dataset used for computing the resulting accuracy using a fivefold cross validation scheme. The folds used in this paper are the same as the ones used during the challenge. \ja{Why are we describing the dataset here in the background section? Wouldn't it be more appropriate under experiments?}

There are also two larger datasets: the
Rouen dataset \cite{rakotomamonjy2015histogram} and the public part of the DCASE2016 challenge \cite{Mesaros2016_EUSIPCO}. The latter is also considered in this paper as a validation of the proposed approach. \ja{What does this last sentence mean?}

The DCASE2013 dataset has significant intra-class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices \cite{lagrange:hal-01082501}. In addition, it is still challenging, with a state-of-the-art system based on feature design \ja{?} and SVMs achieving $76\%$ \cite{roma2013} (winner of the DCASE2013 challenge). Another system, using a HOG+SVM approach \cite{rakotomamonjy2015histogram}, achieves $75\%$ and $92\%$ on the DCASE2013 and Rouen datasets, respectively. Recent advances using hierarchical classifier architectures obtain between $84\%$ and $87\%$ on DCASE2013 depending on the prior knowledge used during training \cite{phan2016label}. On the Rouen dataset, the state-of-the-art is currently $95\%$ \cite{bisot2016acoustic}.

In this paper, we shall demonstrate that the use of features based on the wavelet scattering transform together with object-based representation of the acoustic scene allows us to achieve state-of-the-art \ja{?} performance in both the ASSR and ASC paradigms.
